% LaTeX resume using res.cls
%
% Millar Resume, \LaTex style
%

\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage[pdftex]{graphicx}
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf David W Millar}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{140 Levering Street}
 \moveleft.5\hoffset\centerline{Philadelphia, PA 19127}
 \moveleft.5\hoffset\centerline{david.w.millar@gmail.com}
 \moveleft.5\hoffset\centerline{http://www.github.com/david-w-millar}
 \moveleft.5\hoffset\centerline{610.304.8828}


\begin{resume}

\section{Summary}
  Seasoned software engineer with insatiable technolust.  Eager to ``make the impossible possible, the possible easy, and the easy elegant.''
  Well versed in OOA/D, web application architecture and infrastructure, security, the jvm ecosystem, networks, SOA and Integration systems.
  Experience supporting the full systems development life-cycle and integration of production enterprise applications, public facing multi-tenant cloud applications, research oriented projects, and open source projects.
  Invested in agile practices, continuous process improvement, automation, and DevOps.
\section{Experience}

  {\sl Senior Software Engineer} \hfill Sept 2012  -- Present \\
  IBM Smarter Workforce\\
  Wayne, PA
  \begin{itemize} \itemsep -2pt
    \item Designed, developed, and maintained greenfield core infrastructure services, including SSO and other centralized auth related responsibilities.
    \item Mentored juniors, seniors, and directors across departments including QA, software engineering, and database administration on topics such as automated functional web testing, behavior driven and test driven development, automated database change management solutions.  Presented to cross functional teams on pragmatic DevOps, technical debt and refactoring.
    \item Pushed for and educated about polyglot persistence where performance or design warranted it.
  \end{itemize}

  {\sl Senior Software Engineer} \hfill March 2012  -- July 2012 \\
  {\sl Software Engineer Contractor} \hfill Dec 2011 -- March 2012 \\
  MDconnectME Inc \\
  Philadelphia , PA
  \begin{itemize} \itemsep -2pt
    \item Worked in a senior capacity on planning, design, requirements, developing and maintaining infrastructure, from the ground up, for the MDconnectME cloud application. Which has been featured in a New York Times blog, Fox Business, MSN News, and various local media outlets.  (JEE/Spring/Hibernate/Jsp/jQuery based application).
    \item Many hats were worn: data architecture, security, UX, etc.  Major focus on simplicity, scalability, cross-browser support, and HIPAA compliance.
    \item Designed, developed, and maintained back-end messaging systems and infrastructure using Amazon EC2 and Twillio for SMS and e-mail.
  \end{itemize}


  {\sl Software Engineer} \hfill  June 2011 -- March 2012 \\
    Yellowbook Inc \\
    King of Prussia, PA
    \begin{itemize} \itemsep -2pt
      \item Developed and maintained software systems to manage Yellowbook's repository of digital business listings, advertisements, and related artifacts along with a web application for data management.
            Interfaced with several other systems including the CDN, artwork workflow, search, web, in-house ratings and review system, and billing.
      \item Managed an off-shore development team of three.
      \item Had the team adopt Behavior-Driven Development tools, which allowed business analysts to write automated software tests in a subset of plain English.
      \item Ported a set of ETL applications from C\# to Java, which managed data feeds to third parties, including Google, Citygrid, and TomTom.
      \item Struggled with the ennui of legacy application maintenance, and technophobes in leadership who were uncomfortable deviating from the known to the productive.
    \end{itemize}


  {\sl Research Engineer} \hfill  November 2008 -- April 2011 \\
    Drexel University ACIN Center \\
    Camden, NJ
    \begin{itemize}  \itemsep -2pt
      \item Managed and oversaw the completion of several projects under contract with the DoD and assisted in writing proposals to acquire multi-million dollar contracts.  Main focus was distributed messaging systems for SOA and intelligent agent based C\textsuperscript{2} (Command and Control) applications. Other work included Biometric profile dissemination software.
      \item Researched, developed, and analyzed reliable group messaging systems for resource constrained networks using best of breed network emulation tools.  Investigation areas included proactive vs reactive and hybrid service discovery approaches, and translating client/server software to use a peer-to-peer paradigm.
      \item The primary output of the research was a system called XOP (XMPP Overlay Proxy), which was a greenfield XMPP server implementation with several extensions that provided a peer-to-peer implementation of a subset of the XMPP protocol and extensions.  This has since been ported to Android. Also developed integration layer for legacy DoD messaging systems.
      \item Received a research award from the Naval Research Labs for a paper that analyzed the performance of this system, which is now on the fast track to deployment in the field.
      \item Participated in live Command, Control, Communications, Computers, Intelligence, Surveillance and Reconnaissance (C\textsuperscript{4}ISR) exercises  with domestic forces. Supported coalition experiments with the German and French governments.
    \end{itemize}


  {\sl Software Engineer} \hfill  September 2003 -- November 2008 \\
    Resource Utilization and Management Group \\
    Comcast, Mount Laurel, NJ
    \begin{itemize}  \itemsep -2pt
      \item Developed reporting, visualization, and integration layer for IP address utilization. Used for daily operations and to automate ARIN report generation to satisfy requirements for acquiring more address space. (perl, gd, mysql, php, apache httpd, ActiveMQ, JEE, Spring, Struts, Velocity)
      \item Worked with consultants to develop and optimize an IP Address Management System supporting over 2,000 users and hosting information for Comcast's national infrastructure and millions of customers.
      \item Developed software to mass import network addressing information from acquisitions.
    \end{itemize}


\section{Education} {\sl Bachelor of Science,} Computer Science \\
   % \sl will be bold italic in New Century Schoolbook (or any postscript font) and just slanted in Computer Modern (default) font
   Drexel University, Philadelphia, PA \\
   Concentrations: Data Structures and Algorithms and Operating Systems


% This needs some serious work
% TODO: Figure out a way to better organize this %
\section{Skills}
\begin{list}{}%
{\leftmargin=1em \itemindent=-1em}
  \item \textbf{\textit{Operating Systems:}} Linux, OS X, Windows, Various Unix, Android
  \item \textbf{\textit{Languages:}} Groovy, Java, Ruby, SQL dialects, \LaTeX, various scripting, markup, and templating. Capable of, and eager to learn new languages (Scala and Python are in the pipeline).
  \item \textbf{\textit{CASE Tools: }}  Intellij IDEA, Eclipse, gradle, maven, ant, svn, mercurial, jenkins/hudson, artifactory, redmine
  \item \textbf{\textit{Frameworks: }}  Grails, Rails, Geb, Spock, angularjs, jQuery, Spring, Hibernate, various web, testing, and AJAX frameworks
  \item \textbf{\textit{Other: }} vim, apache httpd, various application servers, JMS/AMQP, Amazon AWS/EC2, wireshark, nmap, metasploit, XMPP
\end{list}


\section{Publications}
  ``Net-Centric Information and Knowledge Management and Dissemination for Data-to-Decision C2 Applications using Intelligent Agents and Service-Oriented Architectures.'' I. Mayk, W. Regli, D. Nguyen, et al.,  Proceedings of the 2011 Military Communications Conference, Baltimore, MD, 2011. 

  ``An Evaluation of Serverless Group Chat'' Robert N. Lass, Duc N. Nguyen,  Willam C. Regli. Military Communications. 7 November -- 10 November 2011, Baltimore, MD

  ``Client/Server Messaging Protocols in Serverless Environments.'' Justin Dean, Andrew Harrison, Robert N. Lass, Joe Macker, David Millar and Ian Taylor. Journal of Network and Computer Applications, 2011

  ``XO: XMPP Overlay Service for Distributed Chat.'' Robert N. Lass, Joseph P. Macker, David Millar, Willam C. Regli, Ian Taylor. Military Communications. 31 October -- 3 November 2010, San Jose, CA

  ``GUMP: Adapting Client/Server Messaging Protocols into Peer-to-Peer Serverless Environments.'' Robert N. Lass, Joe Macker, David Millar and Ian Taylor Bio-Inspired Algorithms for Distributed Systems 2010 , 7--11 June 2010, Washington, D.C.


\section{Professional Organizations}
  {\it Association for Computing Machinery (ACM)} \\
  Member since 2012

  {\it Electronic Frontier Foundation (EFF)} \\
  Gold Member since 2011

  {\it Upsilon Pi Epsilon} \\
  International Honor Society for the Computing and Information Disciplines

\section{Awards And Honors}
  {\it Alan Berman Research Publication Award} \\
  Naval Research Labs, 2012

\section{Current Interests}
  High Signal-To-Noise Ratio Development: convention over configuration, domain-specific language design, expressive and literate programming. \\
  DevOps, build/test/release/deployment automation, and configuration management. \\
  General hackery.

\end{resume}


\end{document}

